Interpretable Machine Learning

### 2021-06-21 chunks/story-wines.Rmd
add bliz talk

## Accumulated Local Effects

```{r,  out.width = '78%'}
knitr::include_graphics("../images/ale-intuition-1.jpg")
```

## Accumulated Local Effects

```{r,  out.width = '78%'}
knitr::include_graphics("../images/ale-intuition-2.jpg")
```

## Accumulated Local Effects

```{r,  out.width = '78%'}
knitr::include_graphics("../images/ale-intuition-3.jpg")
```

## Accumulated Local Effects
```{r,  out.width = '78%'}
knitr::include_graphics("../images/ale-intuition-4.jpg")
```

## Accumulated Local Effects
```{r,  out.width = '78%'}
knitr::include_graphics("../images/ale-intuition-5.jpg")
```

## Effect of Alcohol
```{r}
eff = FeatureEffect$new(pred, "alcohol", method = 'ale')
plot(eff)
```

## Effect of Volatile Acidity
```{r}
eff = FeatureEffect$new(pred, "volatile.acidity", method = 'ale')
plot(eff)
```

@@

```{r}
effs = FeatureEffects$new(pred)
plot(effs, ncols = 4)
```

>>>>

## ICE and PDP

```{r,  out.width = '72%'}
knitr::include_graphics("../images/pdp.gif")
```

## Effect of Alcohol
```{r}
eff = FeatureEffect$new(pred, "alcohol", method = 'pdp+ice')
plot(eff)
```

## Effect of Volatile Acidity
```{r}
eff = FeatureEffect$new(pred, "volatile.acidity", method = 'pdp+ice')
plot(eff)
```

@@

```{r}
effs = FeatureEffects$new(pred, method = "pdp")
plot(effs, ncols = 4)
```
